Clean spectral data

### 2020-11-06 R/clean_spectral_data.Rmd
results figures
hist with taxonID instead of genusSpecies

# plot histogram with count per genusSpecies. color bars based on whether
# # samples exceeds the threshold
ggplot(taxonCounts, aes(y = reorder(genusSpecies, n), x = n)) + 
                          #reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", aes(fill = countGT)) + 
  labs(title = paste("Histogram of samples per species.",
                     speciesCountTotal, "total species;",
                     speciesCountGT, "species with greater than",
                     thresh, "samples"),
       y = "Scientific Name (Genus + Species)",
       fill = paste("Count >", thresh)) + 
  theme_bw() + 
  scale_fill_manual(values = c("#d95f0e", "#7bccc4"))
```

@@

```{r}
# table with species info and counts

library(taxize)

taxon_info <- all_spectra %>% 
  select(genusSpecies, taxonID) %>% 
  distinct()

taxons_GT <- taxonCounts %>% 
  # keep taxons that have enough samples 
  filter(countGT == TRUE) %>% 
  # remove the column that indicates if the taxon has enough samples
  select(-countGT) %>% 
  # merge in the taxonID information 
  left_join(taxon_info, by="genusSpecies")

# for(i in 1:nrow(taxons_GT)){
#   print(i)
#   taxize::sci2comm(sci = taxons_GT[i]$genusSpecies)
# }

```

@@

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 11)
```

>>>>

# plot histogram with count per genusSpecies. color bars based on whether
# # samples exceeds the threshold
ggplot(taxonCounts, aes(y = reorder(genusSpecies, n), x = n)) + 
                          #reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", aes(fill = countGT)) + 
  labs(title = paste("Histogram of samples per species.",
                     speciesCountTotal, "total species;",
                     speciesCountGT, "species with greater than",
                     thresh, "samples"),
       y = "Scientific Name (Genus + Species)",
       fill = paste("Count >", thresh)) + 
  theme_bw() + 
  scale_fill_manual(values = c("#d95f0e", "#7bccc4"))
```
Histogram using scientific name

```{r fig.width=9, fig.height=12, eval=FALSE, include=FALSE}
# Histogram with just the taxons that have enough samples 
samplesCountGT <- taxonCounts %>% 
  filter(countGT == TRUE)

@@

```{r}
# table with species info and counts 
taxon_info <- all_spectra %>% 
  select(genusSpecies, taxonID) %>% 
  distinct()

taxons_GT <- taxonCounts %>% 
  # keep taxons that have enough samples 
  filter(countGT == TRUE) %>% 
  # remove the column that indicates if the taxon has enough samples
  select(-countGT) %>% 
  # merge in the taxonID information 
  left_join(taxon_info, by="genusSpecies")
```

Histogram using taxon code?

ggplot(distinct(taxons_GT, genusSpecies, .keep_all=TRUE), 
       aes(y = reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", fill = "#7E9E8F") + 
  labs(y = "Taxon code\n",
       x = "\nNumber of spectra") + 
  #theme(axis.text = element_text(size = 12)) +
  theme_bw(base_size=16)

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 9, height = 10)
```

@@

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 10)
```
